Instructions for ACL-IJCNLP 2021 Proceedings

### 2021-06-03 reports/SemDial2021/semdial.tex
svg image
examples, references

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

\usepackage{booktabs}
\usepackage{tabularx}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{natbib}

@@

@@

\bibliographystyle{acl_natbib}
\bibliography{semdial}

%\appendix

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

\usepackage{booktabs}
\usepackage{tabularx}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\usepackage{svg}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabulary}

\usepackage{enumitem}
\newlist{lingex}{enumerate}{3} % easy numbering of examples
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}
\usepackage{adjustbox}

\usepackage{textcomp}
\usepackage{amssymb}

@@

In this section we analyse dialogue acts according to their co-location with
laughter and provide some qualitative insights from the
statistics. The distribution of laughs in different dialogue acts has
a rather uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
most distinct outlier is ``Nonverbal'' dialogue act which is
misleading with respect to laughter, because utterances only
containing a single laughter token fall into this category, however
they can serve, for example, to acknowledge a statement or to deflect
a question \citep{mazzocconi2019phd}.

\begin{figure}
  \includesvg[width=\linewidth]{img/box-swda}
  \caption{Box plot for proportions of dialogue act which contain laughs.}
  \label{fig:box-swda}
\end{figure}

Let us introduce our comparison schema for the other two outliers,
Downplayer and Apology, comparing them with the most common dialogue
act in SWDA---Statement-Non-Opinion.  We take into consideration five
laughter-related dimensions of an utterance, and create 5-dimensional
representations of dialogue acts according to them. Each dimension's
value equals to the proportion of utterances of a given type which
contain laughter.
\begin{itemize}
\item[$\uparrow$] current utterance;
\item[$\nwarrow$] previous utterance by the same speaker;
\item[$\swarrow$] previous utterance by the other speaker;
\item[$\nearrow$] next utterance by the same speaker;
\item[$\searrow$] next utterance by the other speaker.
\end{itemize}

\begin{figure}
  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
  \caption{Comparison of the most common dialogue act in
    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
    of utterances which contain laughter are shown in association with
    each dialogue act. }
  \label{fig:orbit}
\end{figure}

% 1. overview: rather uniform distribution with few outliers
% 2. let's look at outliers
% 3. consider 5 dimensions of relations

For instance, 
\begin{lingex}
\item
  \adjustbox{valign=t}{
    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
    A: & I am so sorry to keep you on hold. & Apology \\
    B: & <Laughter> No problem. & Downplayer \\
    A: & Are you at work? & YN-Quest. \\
  \end{tabulary}}
\end{lingex}

@@

\bibliographystyle{acl_natbib}
\bibliography{semdial}
\appendix
\onecolumn
\section{Supplementary materials}\label{sec:suppl}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}). Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter. Top chart: SWDA, Bottom chart: AMI-DA. }
    \label{fig:by-da}
\end{figure*}
